### 2015-04-15 contract-language.tex
Fixed Grammar.

\item \textbf{Eventual consistency}: Eventually consistent operations can
	be satisfied as long as the client can reach at least one replica. In the
	bank account example, \rcf{deposit} is an eventually consistent operation.
	While an \ecds typically offer \emph{basic} eventual consistency with all
	possible anomalies, we assume that our store provides stronger semantics that
	remain highly-available~\cite{BailisHAT,COPS}; the store always exposes a
	\emph{causal cut} of the updates. This semantics can be formally captured in
	terms of the following contract definition:

>>>>

\item \textbf{Eventual consistency}: Eventually consistent operations can
	be satisfied as long as the client can reach at least one replica. In the
	bank account example, \rcf{deposit} is an eventually consistent operation.
	While an \ecds typically offers \emph{basic} eventual consistency with all
	possible anomalies, we assume that our store provides stronger semantics that
	remain highly-available~\cite{BailisHAT,COPS}; the store always exposes a
	\emph{causal cut} of the updates. This semantics can be formally captured in
	terms of the following contract definition:
